Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-19 paper/paper_acm.tex
adding _{\lnot \lnot}

In the previous section, we defined a (countably) infinite family of
modalities $\Type_i \to \Type_i$. One can extend them to whole
$\Type$ by composing with truncation:

@@

We can view sheafification in terms of model of type theory but
because of the resulting modality on $\Type$ is not left exact, we
need to restrict ourselves to a type theory with only one universe.
%
Let $\mathfrak M$ be a model of homotopy type theory with one
universe.
%
Using the modality $\modal$ (for any level $n$) associated to the
sheafification, there is a model $\modal \mathfrak M$ of type theory
with one universe (using results in
Section~\ref{sec:new-type-theory}), where excluded middle is true, and
which is univalent (as shown in Proposition~\ref{prop:univalence}).
%
This model transformation can better be described as a program
transformation, as done in the next section.

>>>>

In the previous section, we have defined a (countably) infinite family of
modalities $\Type_i \to \Type_i$. One can extend them to whole
$\Type$ by composing with truncation:

@@

We can view sheafification in terms of model of type theory but
because of the resulting modality on $\Type$ is not left exact, we
need to restrict ourselves to a type theory with only one universe.
%
Let $\mathfrak M$ be a model of homotopy type theory with one
universe.
%
Using the modality $\modal_{\lnot \lnot}$ (for any level $n$) associated to the
sheafification, there is a model $\modal_{\lnot \lnot} \mathfrak M$ of type theory
with one universe (using results in
Section~\ref{sec:new-type-theory}), where excluded middle is true, and
which is univalent (as shown in Proposition~\ref{prop:univalence}).
%
This model transformation can better be described as a program
transformation, as done in the next section.
